Metadata and Other Structures in texor

### 2023-09-28 supplement/metadata/metadata.tex
Added data about theorem environments.

\section{Summary}
In summary the \CRANpkg{texor} package alongside pandoc supports:
\begin{itemize}
\item Extracting metadata and putting it together well.
\item Handling links, block quotes, citations and footnotes.
\end{itemize}

>>>>

\section{Theorem environments}

\begin{theorem}\label{theorem:1}
This is a sample theorem..
\end{theorem}

\begin{proposition}\label{prop:1}
As with $X \in \mathbb{R}$ this proposition ...  
\end{proposition}

\begin{remark}\label{rm:1}
\CRANpkg{texor} makes the article conversion easier.
\end{remark}

\pkg{Pandoc} supports default LaTeX theorem environments. One can refer to these environments
like Theorem~\ref{theorem:1},Proposition~\ref{prop:1} and Remark~\ref{rm:1} made here.
However custom theorem environments are not supported yet.

\section{Summary}
In summary the \CRANpkg{texor} package alongside pandoc supports:
\begin{itemize}
\item Extracting metadata and putting it together well.
\item Handling links, block quotes, citations and footnotes.
\item Default theorem environments.
\end{itemize}
